\documentclass{statsoc}
% \usepackage[top = 3cm, bottom = 3cm, left = 3cm, right=3cm]{geometry}
\usepackage[a4paper,top=1in, bottom=1in, left=0.95in, right=0.95in]{geometry}
\usepackage{amsmath, amssymb}
\usepackage{arydshln}
\usepackage{enumerate}
\usepackage{setspace}
\usepackage{natbib}
\usepackage{hyperref}
\usepackage{mathtools}
\usepackage{xcolor}
\hypersetup{
  colorlinks=true,
  citecolor=black,
  linkcolor=black}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{graphicx}
% \usepackage{subcaption}
% \graphicspath{{./figs/}}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}%
\newcommand{\xmark}{\ding{55}}%

% \usepackage{xr}
% \externaldocument{conformal_causal_JRSSB_final_supp}

\makeatletter
\renewcommand*{\eqref}[1]{%
  \hyperref[{#1}]{\textup{\tagform@{\ref*{#1}}}}%
}
\makeatother

\newcommand{\const}{B}
\newcommand{\lb}{\left(}
\newcommand{\rb}{\right)}
\newcommand{\td}{\tilde}
\newcommand{\E}{\mathbb{E}}
\newcommand{\cE}{\mathcal{E}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\G}{\mathcal{G}}
\newcommand{\R}{\mathbb{R}}
\renewcommand{\r}{r}
\renewcommand{\O}{\mathcal{O}}
\renewcommand{\P}{\mathbb{P}}
\renewcommand{\S}{\mathcal{S}}
\newcommand{\A}{\mathcal{A}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\Z}{\mathcal{Z}}
\newcommand{\I}{\mathcal{I}}
\newcommand{\eps}{\epsilon}
\newcommand{\qt}{\mathrm{Quantile}}
\newcommand{\lo}{\mathrm{lo}}
\newcommand{\hi}{\mathrm{hi}}
\newcommand{\obs}{\mathrm{obs}}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\tr}{\mathrm{tr}}
\newcommand{\ca}{\mathrm{ca}}
\renewcommand{\sp}{\mathrm{sp}}
\newcommand{\tv}{d_{\mathrm{TV}}}
\newcommand{\CV}{\mathrm{CV}}
\newcommand{\LACI}{\mathrm{LACI}}
\newcommand{\CQR}{\mathrm{CQR}}
\newcommand{\Jackknife}{\mathrm{Jackknife}}
\newcommand{\generic}{\mathrm{generic}}
\newcommand{\train}{\mathrm{train}}
\newcommand{\test}{\mathrm{test}}
\newcommand{\CITE}{\hat{C}_\text{ITE}}
\newcommand{\tdCITE}{\td{C}_\text{ITE}}
\newcommand\indep{\protect\mathpalette{\protect\independenT}{\perp}}
\def\independenT#1#2{\mathrel{\rlap{$#1#2$}\mkern2mu{#1#2}}}
\newcommand{\revision
}[1]{{\color{blue}#1}}

\DeclarePairedDelimiterX{\divpq}[2]{(}{)}{%
  #1\;\delimsize\|\;#2%
}
\allowdisplaybreaks


\numberwithin{equation}{section}

\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{remark}{Remark}
\newtheorem{corollary}{Corollary}


\definecolor{darkgreen}{rgb}{0.0, 0.42, 0.24}
\newcommand{\rev}[1]{\textcolor{red}{#1}}
\newcommand{\ejc}[1]{\textcolor{red}{[EJC: #1]}}
\newcommand{\lihua}[1]{\textcolor{darkgreen}{[Lihua: #1]}}
\newcommand{\allison}[1]{\textcolor{magenta}{[AS: #1]}}
\newcommand{\changed}[1]{\textcolor{blue}{#1}}


\title[Conformal Inference of Counterfactuals and Individual Treatment Effects]{Conformal Inference\\ of Counterfactuals and Individual Treatment Effects}

\author{Lihua Lei}
\address{Department of Statistics, Stanford University}
\email{lihualei@stanford.edu}

\author[Lihua Lei and Emmanuel J. Cand\`{e}s]{Emmanuel J. Cand\`{e}s}
\address{Department of Statistics and Department of Mathematics, Stanford University}
\email{candes@stanford.edu}

\begin{document}

\maketitle

\begin{abstract}
  Evaluating treatment effect heterogeneity widely informs treatment
  decision making. At the moment, much emphasis is placed on the
  estimation of the conditional average treatment effect via flexible
  machine learning algorithms. While these methods enjoy some
  theoretical appeal in terms of consistency and convergence rates,
  they generally perform poorly in terms of uncertainty
  quantification. This is troubling since assessing risk is crucial
  for reliable decision-making in sensitive and uncertain
  environments. In this work, we propose a conformal inference-based
  approach that can produce reliable interval estimates for
  counterfactuals and individual treatment effects under the potential
  outcome framework. For completely randomized or stratified randomized experiments with perfect
  compliance, the intervals have guaranteed average coverage in finite
  samples regardless of the unknown data generating mechanism. For
  randomized experiments with ignorable compliance and general
  observational studies obeying the strong ignorability assumption,
  the intervals satisfy a doubly robust property which states the
  following: the average coverage is approximately controlled if
  either the propensity score or the conditional quantiles of
  potential outcomes can be estimated accurately.  Numerical studies
  on both synthetic and real datasets empirically demonstrate that
  existing methods suffer from a significant coverage deficit even in
  % deceptively 
  simple models. In contrast, our methods achieve the
  desired coverage with reasonably short intervals. %\allison{I think
   % the abstract stinks.}
\end{abstract}

\input{intro}
\input{setup}
\input{counterfactual}
\input{effect}
\input{extension}


\section*{Acknowledgment}
E. C. was supported by Office of Naval Research grant N00014-20-12157. L. L. was supported by NSF OAC grant 1934578. % These results were presented at Stanford on May 7, 2020, and at ONR 2020 Virtual Meeting: predictive and causal modeling --- bridging the gap on June 24, 2020. 
The authors are grateful to David Arbour, Susan Athey, Eytan Bakshy, Stephen Bates, Richard A. Berk, Peter J. Bickel, Jelena Bradic, Andreas Buja, Michael Celentano, Peng Ding, Dean Eckles, Nikolaos Ignatiadis, Yucen Luo, Edward Kennedy, Roger Koenker, Arun Kumar Kuchibhotla, Elizabeth L. Ogburn, Zhimei Ren, Thomas S. Richardson, James Robins, Chiara Sabatti, Jasjeet S. Sekhon, Dylan Small, Sean Taylor, Eric Tchetgen Tchetgen, Yuhao Wang, Jeffrey Wong, Bin Yu, and Xiao-Hua Zhou for their constructive feedback.

\bibliography{conformal_causal}
\bibliographystyle{plainnat}

\clearpage
\appendix

~\\
\begin{center}
  \begin{Large}
    \textbf{Appendix}
  \end{Large}
\end{center}

\input{appendix}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End: